Typing a linear \picalc

### 2020-03-27 paper/paper.tex
Minor stylistic changes

% Constructors
\newcommand{\PO}{\constr{\mathbf{0}}}
\newcommand{\comp}[2]{#1 \; \constr{\parallel} \; #2}
\newcommand{\new}{\constr{\boldsymbol{\nu}} \;}
\newcommand{\send}[2]{#1 \; \constr{\langle} \; #2 \;\constr{\rangle} \;}
\newcommand{\recv}[1]{#1 \; \constr{\mathbb{()}} \;}
\newcommand{\suc}{\constr{\scriptstyle 1+}}
\newcommand{\base}[1]{\constr{B[} \; #1 \; \constr{]}}
\newcommand{\channel}[2]{\constr{C[} \; #1 \; \constr{\propto} \; #2 \; \constr{]}}

@@

% Types
\newcommand{\Set}{\type{SET}}
\newcommand{\reduce}[1]{\; \type{\longrightarrow}_{#1} \;}
\newcommand{\types}[4]{#1 \; \type{\propto} \; #2 \; \type{\vdash} \; #3 \; \type{\boxtimes} \; #4}
\newcommand{\contains}[6]{#1 \; \type{\propto} \; #2 \; \type{[} \; #3 \; \type{]\coloneqq} \; #4 \; \type{\propto} \; #5 \; \type{\boxtimes} \; #6}
\newcommand{\Var}{\type{VAR}}
\newcommand{\Process}{\type{PROCESS}}
\newcommand{\Unused}{\type{UNUSED}}
\newcommand{\PreCtx}{\type{PRECTX}}
\newcommand{\Ctx}{\type{CTX}}
\newcommand{\Type}{\type{TYPE}\;}
\newcommand{\Idx}{\type{IDX}\;}
\newcommand{\Idxs}{\type{IDXS}}
\newcommand{\Carrier}{\type{CARRIER}}
\newcommand{\N}{\type{\mathbb{N}}}
\newcommand{\Channel}{\type{CHANNEL}}
\newcommand{\Rec}{\type{REC}}
\newcommand{\Quantifier}{\type{QUANTIFIER}}
\newcommand{\eq}[1]{\; \type{=}_{#1} \;}
\newcommand{\eqeq}{\; \type{\equiv} \;}

@@

        \inferrule
            {\gamma : \PreCtx_n \\ t : \Type}
            {\gamma , t : \PreCtx_{\suc n}}
  \end{mathpar}

@@

        \inferrule
            {idxs : \Idxs_n \\ idx : \Idx}
            {idxs , idx : \Idxs_{\suc n}}

@@

                \inferrule
                    {\Gamma : \Ctx_{idxs} \\ x : \Carrier_{idx}}
                    {\Gamma , x : \Ctx_{idxs , idx}}
  \end{mathpar}
  \caption{Length-indexed typing contexts; length-indexed index context; index-indexed capability contexts.}
  \label{contexts}
\end{figure}

@@

  \inferrule
      {\gamma : \PreCtx_n \\
        \stacked{idxs : \Idxs_n \\\\ \Gamma : \Ctx_{idxs}}\\
        t : \Type \\
        \stacked{idx : \Idx \\\\ x \; y \; z : \Carrier_{idx}}\\
        \op{x}{y}{z}}
  {\constr{zero} : \contains{\gamma , t}{\Gamma , x}{zero}{t}{y}{\Gamma , z}}

  \inferrule
      {\gamma : \PreCtx_n \\
        \stacked{idxs : \Idxs_n \\\\ \Gamma : \Ctx_{idxs}}\\
        t \; t' \; : Type \\
        \stacked{idx : \Idx \\\\ x : \Carrier_{idx}} \\
        \stacked{idx' : \Idx \\\\ x' : \Carrier_{idx'}} \\
        \Delta : \Ctx_{idxs} \\\\
    loc_x : \contains{\gamma}{\Gamma}{i}{t}{x}{\Delta}}
  {\constr{suc} \; loc_x : \contains{\gamma , t'}{\Gamma , x'}{\suc i}{t}{x}{\Delta , x'}}
\end{mathpar}
\end{adjustwidth}
\caption{This is...}
\end{figure}

@@

  \inferrule
  {t : \Type \\ x : \Carrier_{idx} \\ y : \Carrier_j \\\\
   cont : \types{\gamma , \channel{t}{x}}{\Gamma , y}{P}{\Delta , \lz}}
  {\constr{chan} \; t \; x \; y \; cont : \types{\gamma}{\Gamma}{\new P}{\Delta}}

  \inferrule
  {chan_x : \contains{\gamma}{\Gamma}{i}{\channel{t}{x}}{\li}{\Xi} \\\\
   cont : \types{\gamma , t}{\Xi , x}{P}{\Theta , \lz}}
  {\constr{recv} \; chan_x \; cont : \types{\gamma}{\Gamma}{\recv{i}{P}}{\Theta}}

  \inferrule
  {chan_x : \contains{\gamma}{\Gamma}{i}{\channel{t}{x}}{\lo}{\Delta} \\\\
   loc_y : \contains{\gamma}{\Delta}{j}{t}{x}{\Xi} \\\\
   cont : \types{\gamma}{\Xi}{P}{\Theta}}
  {\constr{send} \; chan_x \; loc_y \; cont : \types{\gamma}{\Gamma}{\send{i}{j}P}{\Theta}}

>>>>

% Constructors
\newcommand{\PO}{\constr{\mathbf{0}}}
\newcommand{\comp}[2]{#1 \; \constr{\parallel} \; #2}
\newcommand{\new}{\constr{\boldsymbol{\nu}} \;}
\newcommand{\send}[2]{#1 \; \constr{\langle} \; #2 \;\constr{\rangle} \;}
\newcommand{\recv}[1]{#1 \; \constr{\mathbb{()}} \;}
\newcommand{\suc}{\constr{\scriptstyle 1+}}
\newcommand{\base}[1]{\constr{B[} \; #1 \; \constr{]}}
\newcommand{\channel}[2]{\constr{C[} \; #1 \; \constr{\propto} \; #2 \; \constr{]}}
\newcommand{\comma}{\; \constr{,} \;}

@@

% Types
\newcommand{\Set}{\type{SET}}
\newcommand{\reduce}[1]{\; \type{\longrightarrow}_{#1} \;}
\newcommand{\types}[4]{#1 \; \type{\propto} \; #2 \; \type{\vdash} \; #3 \; \type{\boxtimes} \; #4}
\newcommand{\contains}[6]{#1 \; \type{\propto} \; #2 \; \type{_[} _{#3} \type{_]=} \; #4 \; \type{\propto} \; #5 \; \type{\boxtimes} \; #6}
\newcommand{\Var}{\type{VAR}}
\newcommand{\Process}{\type{PROCESS}}
\newcommand{\Unused}{\type{UNUSED}}
\newcommand{\PreCtx}{\type{PRECTX}}
\newcommand{\Ctx}{\type{CTX}}
\newcommand{\Type}{\type{TYPE}\;}
\newcommand{\Idx}{\type{IDX}\;}
\newcommand{\Idxs}{\type{IDXS}}
\newcommand{\Carrier}{\type{CARRIER}}
\newcommand{\N}{\type{\mathbb{N}}}
\newcommand{\Channel}{\type{CHANNEL}}
\newcommand{\Rec}{\type{REC}}
\newcommand{\Quantifier}{\type{QUANTIFIER}}
\newcommand{\eq}[1]{\; \type{=}_{#1} \;}
\newcommand{\eqeq}{\; \type{\equiv} \;}

@@

        \inferrule
            {\gamma : \PreCtx_n \\ t : \Type}
            {\gamma \comma t : \PreCtx_{\suc n}}
  \end{mathpar}

@@

        \inferrule
            {idxs : \Idxs_n \\ idx : \Idx}
            {idxs \comma idx : \Idxs_{\suc n}}

@@

                \inferrule
                    {\Gamma : \Ctx_{idxs} \\ x : \Carrier_{idx}}
                    {\Gamma \comma x : \Ctx_{idxs \comma idx}}
  \end{mathpar}
  \caption{Length-indexed typing contexts; length-indexed index context; index-indexed capability contexts.}
  \label{contexts}
\end{figure}

@@

  \inferrule
      {\gamma : \PreCtx_n \\
        \stacked{idxs : \Idxs_n \\\\ \Gamma : \Ctx_{idxs}}\\
        t : \Type \\
        \stacked{idx : \Idx \\\\ x \; y \; z : \Carrier_{idx}}\\
        \op{x}{y}{z}}
  {\constr{zero} : \contains{\gamma \comma t}{\Gamma \comma x}{zero}{t}{y}{\Gamma \comma z}}

  \inferrule
      {\gamma : \PreCtx_n \\
        \stacked{idxs : \Idxs_n \\\\ \Gamma : \Ctx_{idxs}}\\
        t \; t' \; : Type \\
        \stacked{idx : \Idx \\\\ x : \Carrier_{idx}} \\
        \stacked{idx' : \Idx \\\\ x' : \Carrier_{idx'}} \\
        \Delta : \Ctx_{idxs} \\\\
    loc_i : \contains{\gamma}{\Gamma}{i}{t}{x}{\Delta}}
  {\constr{suc} \; loc_i : \contains{\gamma \comma t'}{\Gamma \comma x'}{\suc i}{t}{x}{\Delta \comma x'}}
\end{mathpar}
\end{adjustwidth}
\caption{This is...}
\end{figure}

@@

  \inferrule
  {t : \Type \\ x : \Carrier_{idx} \\ y : \Carrier_{idx'} \\\\
   cont : \types{\gamma \comma \channel{t}{x}}{\Gamma \comma y}{P}{\Delta \comma \lz}}
  {\constr{chan} \; t \; x \; y \; cont : \types{\gamma}{\Gamma}{\new P}{\Delta}}

  \inferrule
  {chan_i : \contains{\gamma}{\Gamma}{i}{\channel{t}{x}}{\li}{\Xi} \\\\
   cont : \types{\gamma \comma t}{\Xi \comma x}{P}{\Theta \comma \lz}}
  {\constr{recv} \; chan_i \; cont : \types{\gamma}{\Gamma}{\recv{i}{P}}{\Theta}}

  \inferrule
  {chan_i : \contains{\gamma}{\Gamma}{i}{\channel{t}{x}}{\lo}{\Delta} \\\\
   loc_j : \contains{\gamma}{\Delta}{j}{t}{x}{\Xi} \\\\
   cont : \types{\gamma}{\Xi}{P}{\Theta}}
  {\constr{send} \; chan_i \; loc_j \; cont : \types{\gamma}{\Gamma}{\send{i}{j}P}{\Theta}}
